\begin{acknowledgements}

The Martinis lab owes its success to the guidance, leadership, and vision of John Martinis.
It has been both an honor and a pleasure to have had the opportunity to conduct my Ph.D. studies in his lab.
I can't imagine a more thorough, rigorous, comprehensive, or illuminating education.  It has been truly transformative.

The greatest gift that an advisor can give his student is to provide a fertile environment in which to study.
John's students have all of the critical resources, equipment, and boundless opportunities, but most importantly we become members of a world class team of scientists.
The experience of being part of this community is irreplaceable.  Thank you.

The success of our project is built on the contributions of each of our team members and depends critically on each person in the lab.
Thank you to everyone for your technical contributions, nourishing conversations, and friendship.
I'm happy that so many of John's students have remained with the group and also that we've added so many great new members.
I'm sure that we have great times ahead!

The first senior scientist that I worked with was Shinobu Ohya.
We had the difficult task of developing a new material system (Titanium Nitride) and understanding how to deposit it to make long coherence devices.
It was an incredible educational experience to work along-side such a skilled material science expert.
I learned a great deal about how to form a comprehensive understanding of a material system during this project.
Working with Shinobu during this formative part of my education gave me a solid foundation for my later years, and I continue to benefit from the experience.
Thank you Shinobu for your guidance and patience as we worked through one of my first graduate school projects.

John once told me that "Once you have learned to measure noise with a qubit every measurement that you make afterward will be easier" and so far he has been right.
In learning to make qubit noise measurements I benefited immensely from the contributions and guidance of Dan Sank.
Dan has a sharpness and clarity in his approach to metrology that is hard to find and extremely valuable.
He is also generous with his time, especially when a younger student is in need.
I've always had a particular fondness for these noise measurements.
Dan, thank you for helping me understand this subtle and beautiful subject.
I'm forever enriched by this knowledge.

Since I joined the gmon team Charles Neill has been my go-to person for technical questions.
Whether I need a quick sanity check on a calculation, help interpreting a data set, or am stuck with direction and need some conceptual brainstorming, a few minutes with Charles generally sorts me out.
%It makes me shudder to think about how far I would still have to go with my Ph.D. if Charles hadn't helped me break through my technical barriers.
%He is also a really nice guy.
Charles, thanks for everything, it has been great working with you.

Pedram Roushan has been my day-to-day mentor for the past few years.
He has also been my day-to-day friend.
Pedram has a deep appreciation for the beauty of physics and it has been a lot of fun to explore quantum dynamics with him.
Pedram's no-holds-barred, get things done, the only true laws are the laws of physics, approach to experimental physics is to be admired.
It certainly keeps things exciting!
Thank you Pedram for your guidance and leadership over these past few years.
I see some beautiful physics on the horizon, and a few day trips with our families too.

Mom and Dad if I were to point to a single determining factor in the success of my Ph.D. it would be the Midwestern work ethic that I got from you.
I feel that I am the most fortunate person in the world because of all of the opportunities and support that I had growing up.
I know that it's not easy to keep two kids in full time activities 12 months per year, in addition to your jobs.
We had a lot of fun along the way and you gave me an excellent foundation for a fruitful life.
The "Throwback Thursdays" are great reminders of these times and provide continuous inspiration for raising my own family so that I can send Thursday messages to my kids in the future.
I can't wait to retrace a few of those summer vacations with Alison, Fiona, Leo, and Naomi.

Many people say that they "would do anything for their children", but few go as far as leaving their jobs and moving across the country for a year just to be a bigger part of their children's lives and help out.
Thank you for your continuing support and effort at staying connected with us,
whether it is timing your visits for when we have a childcare gap or the weekend video calls that you have with the kids.

Thank you especially for your friendship throughout graduate school.
Our phone calls keep me in good spirits and I know that I can count on good advice when I need it most.

Chris and Robin, I appreciate the kindness that you've shown me and especially the help with our kids.
The kids always look forward to your weekend video calls.  You can't imagine how helpful it is when you make a long weekend visit to help when the kids are out of school.
I'm looking forward to more family time after graduation and it will be great to see more of you, whether it's evening card games or activities with the kids.
Thank you for your support.

Nick, you're my brother and my best friend.
Through thick and through thin, brothers are blood.
I'm proud to call you my brother and feel an extra boost of confidence knowing that I have you in my corner.
Thanks for your support and friendship, I'm looking forward to spending more time with you after I graduate.

A graduate degree requires as much commitment from the family as from the student.
Thank you Alison, Fiona, Leo, and Naomi for making the journey with me.
You've brought friendship, joy, and fulfillment into my life.
You give me meaning and purpose as well as hope and happiness.
I'm very thankful for your contributions and am looking forward to sharing the next phase of life with you all.
Having a family is truly life's greatest joy.
I love you.

\end{acknowledgements}
